Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-24 doc/bcspaper/article.tex
Added reference to Maria's CoreSC paper to the bibliography. Made some general cuts and rephrasings in introduction

However, the document title is just one of the crucial parts of a scientific
paper's structure.  Liakata \emph{et al.} (2012) describe a system for
automatically processing and classifying sentences in a research paper
according to the core scientific concept (CoreSC) that they
describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis},
{\em Goal}, {\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.
CoreSC labels can be allocated to all sentences in a scientific paper in order
to identify which scientific concept each sentence encapsulates.  SAPIENTA
(\url{http://www.sapientaproject.com}) is a publicly available machine learning
application which can automatically annotate all sentences in a scientific
paper with their CoreSC labels. It was trained using a corpus of physical
chemistry and biochemistry research papers whose sentences were manually
annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic
information retrieval system can use this information in order to provide
better filtering and search capabilities for researchers.  Partridge {\st the
ability to search for phrases and keywords by CoreSC will facilitate}
implements such context-aware keyword search, by allowing researchers to search
for papers where a term appears in sentences with a specific CoreSC label (e.g
only in {\em Method} senetences). This can be used to greatly improve both the
precision with which researchers are able to perform searches for scientific
literature and the accuracy of those searches in terms of relevance to the
reader.

>>>>

However, the document title is just one of the crucial parts of a scientific
paper's structure.  Liakata \emph{et al.} (2012) describe a system for
automatically processing and classifying sentences in a research paper
according to the core scientific concept (CoreSC) that they
describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis},
{\em Goal}, {\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.
CoreSC labels can be allocated to all sentences in a scientific paper in order
to identify which scientific concept each sentence encapsulates.  SAPIENTA
(\url{http://www.sapientaproject.com}) is a publicly available machine learning
application which can automatically annotate all sentences in a scientific
paper with their CoreSC labels. It was trained using a corpus of physical
chemistry and biochemistry research papers whose sentences were manually
annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic
information retrieval system can use this data to provide better filtering and
search capabilities for researchers.  Partridge implements such context-aware
keyword search, by allowing researchers to search for papers where a term
appears in sentences with a specific CoreSC label (e.g only in {\em Method}
senetences). This can be used to greatly improve both the precision with which
researchers are able to perform searches for scientific literature and the
accuracy of those searches in terms of relevance to the reader.
